Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-29 bbbq_article.tex
Put TMH-derived epitopes figures into one with two panels.

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_grid.png}
  \caption{
    Percentage of MHC-I epitopes predicted to be overlapping with TMHs
    for the proteomes of human, SARS-CoV-2 and \emph{M. tuberculosis}.
    The dashed horizontal lines indicate the percentage as expected by chance.
    See supplementary table \ref{tab:tmh_binders_mhc1} for the exact TMH and epitope counts.
    \richel{Add panel with hydrophobicity}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.8\textheight]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_grid.png}
  \caption{
    Percentage of MHC-II epitopes predicted to be overlapping with TMHs
    for a human, viral and bacterial proteome.
    The dashed horizontal lines indicate the percentage as expected by chance.
    See supplementary table \ref{tab:tmh_binders_mhc2} for the exact TMH and epitope counts.
  }
  \label{fig:2}
\end{figure}

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_grid.png}
    \label{fig:1}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=\linewidth]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_grid.png}
    \label{fig:2}
  \end{subfigure}
  \caption{
    TMH-derived peptides are predicted to be over-presented in MHC-I (left
    panel) and MHC-II (right panel).
    Both panels show the percentage of epitopes predicted to be 
    overlapping with TMHs
    for the proteomes of human, SARS-CoV-2 and \emph{M. tuberculosis}.
    The dashed horizontal lines indicate the percentage as expected by chance.
    See supplementary tables \ref{tab:tmh_binders_mhc1} and \ref{tab:tmh_binders_mhc2}
    for the exact TMH and  epitope counts.
    \richel{Add panel with hydrophobicity}
  }
\end{figure}

%\begin{figure}[!htbp]
%  \includegraphics[height=0.9\textheight]{bbbq_1_smart_results/fig_f_tmh_mhc1_2_grid.png}
%  \caption{
%    Percentage of MHC-I epitopes predicted to be overlapping with TMHs
%    for the proteomes of human, SARS-CoV-2 and \emph{M. tuberculosis}.
%    The dashed horizontal lines indicate the percentage as expected by chance.
%    See supplementary table \ref{tab:tmh_binders_mhc1} for the exact TMH and epitope counts.
%    \richel{Add panel with hydrophobicity}
%  }
%  \label{fig:1}
%\end{figure}
%
%\begin{figure}[!htbp]
%  \includegraphics[height=0.8\textheight]{bbbq_1_smart_results/fig_f_tmh_mhc2_2_grid.png}
%  \caption{
%    Percentage of MHC-II epitopes predicted to be overlapping with TMHs
%    for a human, viral and bacterial proteome.
%    The dashed horizontal lines indicate the percentage as expected by chance.
%    See supplementary table \ref{tab:tmh_binders_mhc2} for the exact TMH and epitope counts.
%  }
%  \label{fig:2}
%\end{figure}

@@
